(Re)building cooperation: Effects of a cognitive intervention on

### 2024-04-19 supplement.Rmd
ready for submission

bibliography: "bib/cogIntervention.bib"
biblio-style: spphys

@@

@@

```{r preDefectionModel,fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  pre-defection trials", fig.align='center'}

@@

>>>>

bibliography: "bib/cogIntervention.bib"
# biblio-style: spphys
csl: nature-no-superscript.csl

@@

We fit the above linear mixed effects model to all trials prior to the pre-programmed defection by the HMM investor (occurring on round 12 pre-manipulation, and round 13 post). A summary of results can be seen in Figure \ref{fig:preDefectionModel}.

@@

```{r preDefectionModel, fig.cap = "Summary of results of a Mixed-effects model fitted to participants returns restricted to  pre-defection trials", fig.align='center'}

@@

In the same way, we fit the linear mixed effects model to all post-defection trials by the HMM investor, including the round on which the defection occurs. A summary of results is presented in Figure \ref{fig:postDefectionModel}
